Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm} Stagnating State Funding for Higher Education and its Effect on Faculty

### 2024-11-15 text/paper.tex
minor mistake addressed.  In need of writing overhaul, to be actioned upon.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy\thanks{
        For helpful comments I thank
        Levon Barseghyan,
        Francine Blau,
        Romain Campbell,
        Maddalena Davoli,
        Ryan Dycus,
        Ronald Ehrenberg,
        Michael Lovenheim,
        Jake Meyer,
        Douglas Miller,
        and Evan Riehl.
        I thank seminar participants at Cornell University (2023, 2024), and the Eastern Economic Association Annual Meetings (2024) for helpful discussion.
        This project's repository, including all materials and anonymised data needed for replication, is made publicly available: 
        \url{https://doi.org/10.5281/zenodo.11373226}.
        Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the \href{https://github.com/shoganhennessy/state-funding-faculty/}{Github project}.
    } \\
    \vspace{0.1cm}
    Economics Department, Cornell University\footnote{
        Address: Uris Hall \#447, Economics Department, Cornell University NY 14853 USA.
    }
}
% Title
\title{Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm}
    Stagnating State Funding for Higher Education and its Effect on Faculty}
\date{First version: 1 September 2022 \\ \vspace{0.15cm}
    This version: \today \\ \vspace{0.15cm}
    \href{https://github.com/shoganhennessy/state-funding-faculty/blob/main/state-funding-faculty-2024.pdf}{Newest version available here.}
    \\ \vspace{-0.5cm}
}
\rhead{\today}
\lhead{Less Funding, More Lecturers, and Fewer Professors.}
% Begin
\begin{document}
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \noindent
    \input{sections/00-abstract.tex}
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy\thanks{
        For helpful comments I thank
        Levon Barseghyan,
        Francine Blau,
        Romaine Campbell,
        Maddalena Davoli,
        Ryan Dycus,
        Ronald Ehrenberg,
        Michael Lovenheim,
        Jake Meyer,
        Douglas Miller,
        and Evan Riehl.
        I thank seminar participants at Cornell University (2023, 2024), and the Eastern Economic Association Annual Meetings (2024) for helpful discussion.
        This project's repository, including all materials and anonymised data needed for replication, is made publicly available: 
        \url{https://doi.org/10.5281/zenodo.11373226}.
        Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the \href{https://github.com/shoganhennessy/state-funding-faculty/}{Github project}.
    } \\
    \vspace{0.1cm}
    Economics Department, Cornell University\footnote{
        Address: Uris Hall \#447, Economics Department, Cornell University NY 14853 USA.
    }
}
% Title
\title{Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm}
    Stagnating State Funding for Higher Education and its Effect on Faculty}
\date{First version: 1 September 2022 \\ \vspace{0.15cm}
    This version: \today \\ \vspace{0.15cm}
    \href{https://github.com/shoganhennessy/state-funding-faculty/blob/main/state-funding-faculty-2024.pdf}{Newest version available here.}
    \\ \vspace{-0.5cm}
}
\rhead{\today}
\lhead{Less Funding, More Lecturers, and Fewer Professors.}
% Begin
\begin{document}
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \noindent
    \input{sections/00-abstract.tex}
\end{abstract}
